Differentially Private Bayesian Inference

### 2018-04-19 main.tex
update plot
update plots

\subsection{Accuracy Study with Hellinger Distance}
\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 200$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
  \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
    \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
\caption{The experimental results of accuracy of four algorithms}
\label{fig_data}
\end{center}
\end{figure*}

We study the accuracy property of the exponential mechanism with three kind of sensitivity, as well as the Laplace mechanism for comparison. As in Fig. \ref{fig_data}, the two figures shown the accuracy of four algorithms under same configuration. The accuracy is measured by Hellinger distance between output $r^*$ and the true inference result $\bysinfer(x)$, $\hlg(r^*, \bysinfer(x))$.

>>>>

\subsection{Accuracy Study Based on Hellinger Distance}
% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% \caption{The experimental results of accuracy of four algorithms}
% \label{fig_data}
% \end{center}
% \end{figure*}

\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
\label{fig_beta_hellinger}
\end{center}
\end{figure*}

We study the accuracy property of the exponential mechanism with three kind of sensitivity, as well as the Laplace mechanism for comparison. As in Fig. \ref{fig_beta_hellinger}, the two figures shown the accuracy of four algorithms under same configuration. The accuracy is measured by Hellinger distance between output $r^*$ and the true inference result $\bysinfer(x)$, $\hlg(r^*, \bysinfer(x))$.

Then, we extended the $\betad$ to the Bernoulli distribution, got the result in Fig. \ref{fig_dirichlet_hellinger}
\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
\label{fig_dirichlet_hellinger}
\end{center}
\end{figure*}

\subsection{Accuracy Study Based on L1 Norm Distance}
For comparison, we study the accuracy of these four mechanisms based on l1 norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig. \ref{fig_dirichlet_hellinger_l1}.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
  \subfigure[accuracy measurement based on l1 norm]{
    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and l1 norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
\label{fig_dirichlet_hellinger_l1}
\end{center}
\end{figure*}
